\documentclass[12pt,a4paper,oneside]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{hyperref}
\hypersetup{
    pdftitle={Mobile and IoT Application Development},%
    pdfauthor={Toksaitov Dmitrii Alexandrovich},%
    pdfsubject={Syllabus},%
    pdfkeywords={syllabus;}{mobile;}{IoT;}{application;}{development},%
    colorlinks,%
    linkcolor=black,%
    citecolor=black,%
    filecolor=black,%
    urlcolor=black
}

\newcommand{\R}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\begin{document}

    \title{Mobile and IoT Application Development}
    \author{
        International University of Central Asia\\
        Information Technology Program
    }
    \date{}
    \maketitle

    \section{Course Information}

        \begin{description}
            \item[Course Repositories]\hfill\\
                \url{https://github.com/iuca/iuca-droid}
            \item[Class Discussions]\hfill\\
                \url{https://piazza.com/iuca.kg/fall2018/iuca-droid}
            \item[Place]\hfill\\
                TBD
            \item[Time]\hfill\\
                TBD
        \end{description}

    \section{Prerequisites}

        TBD

    \section{Contact Information}

        \begin{description}
            \item[Instructor]\hfill\\
                Toksaitov Dmitrii Alexandrovich\\
                \href{mailto:toksaitov_d@iuca.kg}{toksaitov\_d@iuca.kg}
            \item[Office]\hfill\\
                TBD
            \item[Office Hours]\hfill\\
                TBD
        \end{description}

    \section{Course Overview}

This course introduces students to development tools and APIs to build
applications for the Google Android operating system to manage
networks of physical devices, vehicles, home appliances, and other
items embedded with electronics, sensors, and actuators. Students will
get introduced to embedded development on the Arduino platform with
the help of ESP8266, ESP32, and several other WiFi, Bluetooth, and
LoRa-enabled chips with programmable microcontrollers. Students will
also learn how to build unique interactive user interfaces for
multi-touch mobile devices on the Android platform to manage embedded
devices around us. The mobile development part covers object-oriented
design using the Model-View-Controller paradigm, the Java programming
language for the Android Runtime, development frameworks, device
emulators, and application build tools. Other topics include
multi-threading, power and performance considerations, the accelerated
2-D and 3-D graphics APIs. By bringing two platforms together,
students will prototype appliances that can be controlled through
mobile phones to help people with their daily life. The course
projects range from building a simple smart light bulb to an automatic
data collection system with a toy car robot for an indoor positioning
system.

    \section{Topics Covered}

        \begin{itemize}
            \item Development tools (Android Studio, SDK, device emulators)
            \item App. fundamentals (activities, services, content providers)
            \item User interface elements
            \item Graphics and animation
            \item Data storage
            \item Connectivity
            \item Media and camera
            \item Working with device sensors
            \item Publishing and distributing applications
            \item Basics of Digital Electronics
            \item The Arduino IDE
            \item Working with the ESP8266, ESP-32 boards
        \end{itemize}

    \section{Practice Tasks}

        Students are required to finish several practice tasks. The tasks are based
        on topics discussed during lectures.

    \section{Course Project}

        Each student will have to develop an app for the Android platform and a connected device. The
        challenge of the project is to maintain a certain level of quality for
        the application to be able to publish it to end users on Google Play
        Store at the end of the course.

    \section{Final Exam}

        At the end of the course, students have to take the final examination to defend their
        practice works together with the course project.

    \section{Reading}

        \begin{enumerate}
        	\item The Big Nerd Ranch Guide by Bill Phillips, Brian Hardy (ISBN: 978-0321804334)
            \item Introduction to Java Programming, Comprehensive, 11th Edition by Y.
            Daniel Liang (ISBN: 978-0132130806)
        \end{enumerate}

        \subsection{Supplemental Reading}

            \begin{enumerate}
                \item Introduction to Android Application Development: Android
                Essentials, 5th Edition by Joseph Annuzzi Jr., Lauren Darcey, Shane
                Conder (ISBN: 978-0134389455)
                \item Design Patterns: Elements of Reusable Object-Oriented
                Software by Erich Gamma, Richard Helm, Ralph Johnson, John
                Vlissides (ISBN: 978-0201633610)
                \item Refactoring: Improving the Design of Existing Code by
                Martin Fowler, Kent Beck, John Brant, William Opdyke, Don
                Roberts (ISBN: 978-0201485677)
            \end{enumerate}

    \section{Grading}

        \begin{itemize}
            \item Practice tasks (40\%)
            \item Course project (60\%)
        \end{itemize}

        \begin{itemize} \itemsep-10pt \parskip0pt \parsep0pt
            \item[--] 90\%--100\%: A\\
            \item[--] 80\%--89\%: A-\\
            \item[--] 70\%--79\%: B+\\
            \item[--] 65\%--69\%: B\\
            \item[--] 60\%--64\%: B-\\
            \item[--] 56\%--59\%: C+\\
            \item[--] 53\%--55\%: C\\
            \item[--] 50\%--52\%: C-\\
            \item[--] 46\%--49\%: D+\\
            \item[--] 43\%--45\%: D\\
            \item[--] 40\%--42\%: D-\\
            \item[--] Less than 39\%: F
        \end{itemize}

    \section{Rules}

        Students are required to follow the rules of conduct of the Information Technology Program and International University of Central Asia.

        Team work is NOT encouraged. Equal blocks of code or similar structural
        pieces in separate works will be considered as academic dishonesty and
        all parties will get zero for the task.

\end{document}

